A Comparative Quality Metric for Untargeted Fuzzing with Logic State Coverage

### 2024-06-03 paper/main.tex
sec4.2, discussion

\autoref{f:repr} shows an example control-flow graph and its logic space,
gridded up by the different hit counts of the branch $b_1$, $b_2$, and $b_3$.
%, where $m(b)$ denotes the hit count of a branch $b$. 
Each colored box represents one logic state that includes all program
behaviors that exhibit the branch hit counts at the enclosed grid points.
For example, a program behavior that does not hit any of $b_1$, $b_2$, and $b_3$ 
(i.e., $m(b_1)=m(b_2)=m(b_3)=0$) falls into the \cbox{black} logic state, while
all program behaviors that hit only $b_1$ (i.e., $m(b_1)>1$ and
$m(b_2)=m(b_3)=0$) fall into the \cbox{red} logic state.
%, and all program behaviors that hit only $b_2$ and $b_3$ (i.e.,
%$m(b_1)>1$, $m(b_2)>1$, and $m(b_3)=0$) fall into the \cbox{cyan} logic state.

>>>>

\autoref{f:repr} shows an example control-flow graph and its logic space,
gridded up by the different hit counts $m(b)$ of the branch $b_1$, $b_2$, and $b_3$.
%, where $m(b)$ denotes the hit count of a branch $b$. 
Each colored box represents one logic state that includes all program
behaviors that exhibit the branch hit counts at the enclosed grid points.
For example, a program behavior that does not hit any of $b_1$, $b_2$, and $b_3$ 
(i.e., $m(b_1)=m(b_2)=m(b_3)=0$) falls into the \cbox{black} logic state, while
all program behaviors that hit only $b_1$ (i.e., $m(b_1)>1$ and
$m(b_2)=m(b_3)=0$) fall into the \cbox{red} logic state.
%, and all program behaviors that hit only $b_2$ and $b_3$ (i.e.,
%$m(b_1)>1$, $m(b_2)>1$, and $m(b_3)=0$) fall into the \cbox{cyan} logic state.
